%!TEX root = ../ACEFormat.tex
\section[Thermal Scattering]{Thermal Scattering \SaB}\label{sec:ThermalScattering}

Data from thermal \SaB\ tables provide a complete representation of thermal neutron scattering by molecules and crystalline solids. Cross sections for (coherent and incoherent) elastic and (incoherent) inelastic scattering are found on the tables. A coupled energy/angle representation is used to describe the spectra of inelastically scattered neutrons. Angular distributions for elastic scattering are also provided.

Four unique blocks of data are associated with \SaB\ tables. We now briefly describe each of the four data blocks and reference the sections in which their formats are detailed.

\begin{enumerate}
  \item \textbf{\Block{ITIE}}---contains the energy-dependent incoherent inelastic scattering cross sections. The \Block{ITIE}  always exists. See \Sectionref{sec:ITIEBlock}.
  \item \textbf{\Block{ITCE}}---contains the energy-dependent elastic scattering cross sections. The \Block{ITCE} exists if the material has coherent or incoherent elastic scattering; that is, if \jxs{4}$\neq0$. See \Sectionref{sec:ITCEBlock}.
  \item \textbf{\Block{ITXE}}---contains coupled energy/angle distributions for incoherent inelastic scattering. The \Block{ITXE} always exists. See \Sectionref{sec:ITXEBlock}.
  \item \textbf{\Block{ITCA}}---contains angular distributions for elastic scattering. The \Block{ITCA} exists if \jxs{4}$\neq0$ and \nxs{6}$\neq-1$. See \Sectionref{sec:ITCABlock}.
\end{enumerate}

\subsection{\NXS\ Array}\label{sec:NXSThermalScattering}

\begin{table}[H] \centering
  \caption{\NXS\ array element definitions for thermal scattering \ACE\ Table.}
  \label{tab:NXSThermalScattering}
  \begin{tabular}{rll}
    \toprule
    Element & Name         & Description                                                \\
    \midrule
    1       & ---          & Length of second block of data (\XSS\ array)               \\
    2       & \var{IDPNI}  & Inelastic scattering mode                                  \\
    3       & \var{NIL}    & Inelastic dimensioning parameter                           \\
    4       & \var{NIEB}   & Number of inelastic exiting energies                       \\
    5       & \var{IDPNC}  & Elastic scattering mode (coherent=4, incoherent$\ne$4)     \\
    6       & \var{NCL}    & Elastic dimensioning parameter                             \\
    7       & \var{IFENG}  & Secondary energy mode (discrete=0, skewed=1, continuous=2) \\
            & \ldots       &                                                            \\
    16      & ---          &                                                            \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{\JXS\ Array}\label{sec:JXSThermalScattering}
\begin{table}[H] \centering
  \caption{\JXS\ array element definitions for thermal scattering \ACE\ Table.}
  \label{tab:JXSThermalScattering}
  \begin{tabular}{rll}
    \toprule
    Element  & Name       & Location Description                 \\
    \midrule
    1        & \var{ITIE} & Inelastic energy table               \\
    2        & \var{ITIX} & Inelastic cross sections             \\
    3        & \var{ITXE} & Inelastic energy/angle distributions \\
    4        & \var{ITCE} & Elastic energy table                 \\
    5        & \var{ITCX} & Elastic cross sections               \\
    6        & \var{ITCA} & Elastic angular distributions        \\
             & \ldots     & \\
    32       & ---        & \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Format of Individual Data Blocks}
\subsubsection{\textsf{ITIE} Block}\label{sec:ITIEBlock}

The format of the \Block{ITIE} is given in \Tableref{tab:ITIEBlock}. The index at the start of the block is \startblock{ITIE}=\jxs{1}. Note that \jxs{2}=\jxs{1}+1+$N_{in}$. Linear-linear interpolation is assumed between adjacent energies.

\begin{BlockTable}{ITIE}
  \startblock{ITIE}            & $N_{in}$                           & Number of inelastic energies \\
  \startblock{ITIE}+1          & $E_{in}(l),l=1,\ldots,N_{in}$      & Energies                     \\
  \startblock{ITIE}+1+$N_{in}$ & $\sigma_{in}(l),l=1,\ldots,N_{in}$ & Inelastic cross sections
  \label{tab:ITIEBlock}
\end{BlockTable}

\subsubsection{\textsf{ITCE} Block}\label{sec:ITCEBlock}

The format of the \Block{ITCE} is given in \Tableref{tab:ITCEBlock}. The index at the start of the block is \startblock{ITCE}=\jxs{4}.

\begin{BlockTable}{ITCE}
  \startblock{ITCE}            & $N_{el}$                      & Number of elastic energies \\
  \startblock{ITCE}+1          & $E_{el}(l),l=1,\ldots,N_{el}$ & Energies                   \\
  \startblock{ITCE}+1+$N_{el}$ & $P(l),l=1,\ldots,N_{el}$      & (See below)
  \label{tab:ITCEBlock}
\end{BlockTable}

For incoherent elastic scattering (\nxs{5}$\neq4$),
\begin{equation}
  P(l) = \sigma_{el}(E_{el}(l))
\end{equation}
with linear-linear interpolation between points. For coherent elastic scattering (\nxs{5}$=4$),
\begin{equation}
  P(l) = E\cdot\sigma_{el}(E), \qquad E_{el}(l) \le E < E_{el}(l+1).
  \label{eq:CoherentP}
\end{equation}
In this case, the energies $E_{el}(l)$ correspond to Bragg edges, and between two energies the cross section is determined by inverting \Equationref{eq:CoherentP}:
\begin{equation}
  \sigma_{el}(l) = \frac{P(l)}{E}, \qquad E_{el}(l) \le E < E_{el}(l+1).
\end{equation}
Also note that $\sigma_{el}(E)=0$ below $E_{el}(1)$. However, above $E_{el}(N_{el})$, $\sigma_{el}(E) = P(N_{el})/E$.

\subsubsection{\textsf{ITXE} Block}\label{sec:ITXEBlock}

The format of the coupled energy/angle distribution for incoherent inelastic scattering is governed by the value of \nxs{7}. There are three possibilities:
\begin{description}
  \item[$\nxs{7}=0$] equally-likely discrete cosines and energies
  \item[$\nxs{7}=1$] skewed distribution of discrete cosines and energies
  \item[$\nxs{7}=2$] continuous distribution of energies and equally-likely discrete cosines
\end{description}

The format of the \Block{ITXE} for $\nxs{7}<2$ is given in \Tableref{tab:ITXEBlock}. The index at the start of the block is \startblock{ITXE}=\jxs{3}. For each incident energy from the \Block{ITIE}, $N'=$\nxs{4} discrete outgoing energies are given. For each pair of incident and outgoing energies, $N_\mu=$\nxs{3}+1 discrete cosines are given. The incident inelastic energy grid $E_{in}(l)$ is given in the \Block{ITIE}, and linear-linear interpolation is assumed between adjacent values of $E_{in}$.

\begin{ThreePartTable}
  \begin{TableNotes}
    \item[$\dagger$] \label{tn:nieb} The number of outgoing energies \var{NIEB} is determined as \nxs{4}.
  \end{TableNotes}
  \begin{BlockTable}{ITXE}
  \startblock{ITXE}                       & $E_1^{out}[E_{in}(1)]$                     & First of \var{NIEB}\tnotex{tn:nieb}\ outgoing energies for inelastic scattering at $E_{in}(1)$    \\
  \startblock{ITXE}+1                     & $\mu_l(1\rightarrow 1), l=1,\ldots,N_\mu$  & Discrete cosines for scattering from $E_{in}(1)$ to $E_1^{out}[E_{in}(1)]$    \\
  \startblock{ITXE}+1+$N_\mu$             & $E_2^{out}[E_{in}(1)]$                     & Second of \var{NIEB} outgoing energies for inelastic scattering at $E_{in}(1)$   \\
  \startblock{ITXE}+2+$N_\mu$             & $\mu_l(1\rightarrow 2), l=1,\ldots,N_\mu$  & Discrete cosines for scattering from $E_{in}(1)$ to $E_2^{out}[E_{in}(1)]$    \\
  \multicolumn{1}{c}{\vdots}              & \multicolumn{1}{c}{\vdots}                 & \multicolumn{1}{c}{\vdots}                                                    \\
  \startblock{ITXE}+($N'$-1)(1+$N_\mu$)   & $E_{N'}^{out}[E_{in}(1)]$                  & Second of \var{NIEB} outgoing energies for inelastic scattering at $E_{in}(1)$   \\
  \startblock{ITXE}+($N'$-1)(1+$N_\mu$)+1 & $\mu_l(1\rightarrow N'), l=1,\ldots,N_\mu$ & Discrete cosines for scattering from $E_{in}(1)$ to $E_{N'}^{out}[E_{in}(1)]$ \\
  \midrule
  \multicolumn{3}{l}{(Repeat for all remaining values of $E_{in}$)}
  \label{tab:ITXEBlock}
  \end{BlockTable}
\end{ThreePartTable}

When $\nxs{7}=0$, each of the \nxs{4} discrete outgoing energies for a given incident energy are equally probable. When $\nxs{7}=1$, the selection of the discrete outgoing energies is skewed such that the first two and last two outgoing energies have a lower probability of being selected than all other outgoing energies. The first and last energies have a relative probability of 1, the second and second-to-last energies have a relative probability of 4, and all other energies have a relative probability of 10.

Because the use of discrete outgoing energies and cosines can result in unphysical spikes in the neutron flux spectrum at thermal energies, some Monte Carlo codes attempt to ``smear'' the outgoing energies and cosines to produce a smoother distribution (that more closely approximates a continuous distribution with $\nxs{7}=2$).

\todo[inline]{Describe the format for $\nxs{7}=2$.}

\subsubsection{\textsf{ITCA} Block}\label{sec:ITCABlock}

The format of the \Block{ITCA} is given in \Tableref{tab:ITCABlock}. The index at the start of the block is \startblock{ITCA}=\jxs{6}. For each incident energy from the \Block{ITCE}, $N_\mu=$\nxs{6}+1 discrete cosines are given.

\begin{BlockTable}{ITCA}
  \startblock{ITCA}                     & $\mu_l[E_{el}(1)], l=1,\ldots,N_\mu$      & Discrete cosines for elastic scattering at $E_{el}(1)$ \\
  \startblock{ITCA}+$N_\mu$             & $\mu_l[E_{el}(2)], l=1,\ldots,N_\mu$      & Discrete cosines for elastic scattering at $E_{el}(2)$ \\
  \multicolumn{1}{c}{\vdots}            & \multicolumn{1}{c}{\vdots}                & \multicolumn{1}{c}{\vdots}                             \\
  \startblock{ITCA}+($N_{el}$-1)$N_\mu$ & $\mu_l[E_{el}(N_{el})], l=1,\ldots,N_\mu$ & Discrete cosines for elastic scattering at $E_{el}(N_{el})$
  \label{tab:ITCABlock}
\end{BlockTable}

The incident elastic energy grid $E_{el}(l)$ is given in the \Block{ITCE}. Linear-linear interpolation is assumed between adjacent values of $E_{el}$.
